An Instance Based Reasoning for Empirical Transfer Learning

### 2015-04-08 manuscript.tex
CC Metrics

\begin{document}
  \title{An Instance Based Approach for Empirical Transfer Learning}

@@

In this paper we propose the use of an instance based approach in place of the conventional model based approach.

@@

The mutation policy works by projecting the test instance onto the projective planes and identifying the the plane on which the test instance has the largest scalar projection. The planner then reflects over the vertices of the chosen hyperplane, identifying the \textit{better} vertex among the two. Now, a new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex. This process is repeated for all the test instances that are considered defective.
\section{Experimental Design}
The following section describes the experiments used to measure the performance of WHAT on 10 defect data sets and 6 performance prediction data sets.
\subsection{Data sets}
The data was obtained from the PROMISE repository. For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in \ref{}: \keyword{Apache Ant} (1.5 -- 1.7), \keyword{Apache Camel} (1.2 -- 1.6), \keyword{Apache Ivy} (1.1 -- 2.0), \keyword{JEdit} (4.1 -- 4.3), \keyword{Apache Log4j} (1.0 -- 1.2), \keyword{Apache Lucene} (2.0 -- 2.2), \keyword{PBeans} (1.0 and 2.0), \keyword{Apache POI} (2.0 -- 3.0), \keyword{Apache Synapse} (1.0 -- 1.2), \keyword{Apache Velocity} (1.4 -- 1.6), and \keyword{Apache Xalan-Java} (2.5 -- 2.7). Given the empirical nature of the data, it is important to design an experiment such that the planning phase uses only the \keyword{past} data to learn trends which can then be applied to the \keyword{future} data. Thus for our experiment we use data sets that have at least two consecutive releases. 
\begin{itemize}
\item To generate recommendations for a release $i$, the planner uses releases releases $(i-1)$ and $(i-2)$.
\item The predictor also uses releases $(i-1)$ and $(i-2)$. However, we use SMOTE with re-sampling in order to handle the class imbalance in the data and to prevent the predictor from using the same training data as the planner.
\end{itemize}

>>>>

\begin{document}
  \title{An Instance Based Reasoning for Empirical Transfer Learning}

@@

In this paper we propose the use of an instance based approach in place of the conventional model based approach. Instead of generating solutions and going back to a model to see if the solution has any value, we

@@

The mutation policy works by projecting the test instance onto the projective planes and identifying the the plane on which the test instance has the largest scalar projection. The planner then reflects over the vertices of the chosen hyperplane, identifying the \textit{better} vertex among the two. Now, a new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex. This process is repeated for all the test instances that are considered defective.
\begin{figure*}[htbp!]
  \renewcommand{\baselinestretch}{0.8}\begin{center}
    {\scriptsize
      \begin{tabular}{c|l|p{4.7in}}
        amc & average method complexity & e.g. number of JAVA byte codes\\\hline
        avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
        in class\\\hline
        ca & afferent couplings & how many other classes use the specific
        class. \\\hline
        cam & cohesion amongst classes & summation of number of different
        types of method parameters in every method divided by a multiplication
        of number of different method parameter types in whole class and
        number of methods. \\\hline
        cbm &coupling between methods &  total number of new/redefined methods
        to which all the inherited methods are coupled\\\hline
        cbo & coupling between objects & increased when the methods of one
        class access services of another.\\\hline
        ce & efferent couplings & how many other classes is used by the
        specific class. \\\hline
        dam & data access & ratio of the number of private (protected)
        attributes to the total number of attributes\\\hline
        dit & depth of inheritance tree &\\\hline
        ic & inheritance coupling &  number of parent classes to which a given
        class is coupled (includes counts of methods and variables inherited)
        \\\hline
        lcom & lack of cohesion in methods &number of pairs of methods that do
        not share a reference to an instance variable.\\\hline
        locm3 & another lack of cohesion measure & if $m,a$ are  the number of
        $methods,attributes$
        in a class number and $\mu(a)$  is the number of methods accessing an
        attribute, 
        then
        $lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
        \\\hline
        loc & lines of code &\\\hline
        max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
        in class\\\hline
        mfa & functional abstraction & number of methods inherited by a class
        plus number of methods accessible by member methods of the
        class\\\hline
        moa &  aggregation &  count of the number of data declarations (class
        fields) whose types are user defined classes\\\hline
        noc &  number of children &\\\hline
        npm & number of public methods & \\\hline
        rfc & response for a class &number of  methods invoked in response to
        a message to the object.\\\hline
        wmc & weighted methods per class &\\\hline
        \rowcolor{lightgray}
        defect & defect & Boolean: where defects found in post-release bug-tracking systems.
      \end{tabular}
    }
  \end{center}
  \caption{OO measures used in our defect data sets.  Last line is
    the dependent attribute (whether a defect is reported to  a
    post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

\section{Experimental Design}
The following section describes the experiments used to measure the performance of WHAT on 10 defect data sets and 6 performance prediction data sets.
\subsection{Data sets}
The data was obtained from the PROMISE repository. For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in \ref{}: \keyword{Apache Ant} (1.5 -- 1.7), \keyword{Apache Camel} (1.2 -- 1.6), \keyword{Apache Ivy} (1.1 -- 2.0), \keyword{JEdit} (4.1 -- 4.3), \keyword{Apache Log4j} (1.0 -- 1.2), \keyword{Apache Lucene} (2.0 -- 2.2), \keyword{PBeans} (1.0 and 2.0), \keyword{Apache POI} (2.0 -- 3.0), \keyword{Apache Synapse} (1.0 -- 1.2), \keyword{Apache Velocity} (1.4 -- 1.6), and \keyword{Apache Xalan-Java} (2.5 -- 2.7). Given the empirical nature of the data, it is important to design an experiment such that the planning phase uses only the \keyword{past} data to learn trends which can then be applied to the \keyword{future} data. Thus for our experiment we use data sets that have at least two consecutive releases. 
\begin{itemize}
\item To generate recommendations for a release $i$, the planner uses releases releases $(i-1)$ and $(i-2)$.
\item The predictor also uses releases $(i-1)$ and $(i-2)$. However, we use SMOTE with re-sampling in order to handle the class imbalance in the data and to prevent the predictor from using the same training data as the planner.
\end{itemize}
